\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{listings,lstautogobble}
\usepackage{bussproofs}

\geometry{margin=1in}

\title{CPSC 202 PSET 10}
\author{CPSC 202 student}
\date{11/29/17 5pm}

\begin{document}
\maketitle

\section*{A.10.1: Too many injections}
\begin{enumerate}
  \item[a.] $f: A\rightarrow S$, $g: B\rightarrow S$, and $h: C\rightarrow S$ are all injections, therefore, f(A)=g(B)=h(C) means the ranges are the same.
  \item[b.] k represents the elements in the domain, therefore, the range is equal to k. If n represents the elements in S, the range is represented by $\binom{n}{k}$. 
  \item[c.] Given that their ranges are the same, and k represents the size of the domain, there are k! different ways to write each function, or $k!^3$ injective functions.
\item[d.] Therefore, there are $\binom{n}{k}$ ways to choose a range and $k!^3$ injective functions, and $\binom{n}{k}\cdot k!^3$ different triples of functions f, g, and h, or $n_k\cdot k!^2$.
\end{enumerate}

\section*{A.10.2 Binomial coefficients}
\begin{enumerate}
  \item[] Show that, for any $k, m, n \in \mathbb{N}$ s.t. $0\leq k \leq m\leq n, \binom{n}{m}\binom{m}{k} = \binom{n}{k}\binom{n-k}{m-k}.$ 
    \begin{enumerate}
      \item[a.] Expanding binomial coefficients:
        \begin{itemize}
          \item By definition, $\binom{n}{m} = \frac{n!}{m!\cdot(n-m)!}$
            \\ $\binom{m}{k} = \frac{m!}{k!\cdot(m-k)!}$
            \\ $\binom{n-k}{m-k} = \frac{(n-k)!}{(m-k)!\cdot((n-k)-(m-k))!} = \frac{(n-k)!}{(m-k)!\cdot(n-m)!}$
          \item Therefore, $\binom{n}{m}\binom{m}{k} = \frac{n!\cdot m!}{m!\cdot k!\cdot(n-m)!\cdot(m-k)!}
            = \frac{n!}{k!\cdot(n-m)!(m-k)!}$
            \\and $\binom{n}{k}\binom{n-k}{m-k} = \frac{n!\cdot(n-k)!}{k!\cdot(n-k)!\cdot(m-k)!\cdot(n-m)!}
            = \frac{n!}{k!\cdot(m-k)!\cdot(n-m)!} = \frac{n!}{k!\cdot(n-m)!\cdot(m-k)!}$
        \end{itemize}
    \end{enumerate}
     The two expressions are equal therefore, the statement is true.
\end{enumerate}

\section*{A.10.3 Variable names}
\begin{enumerate}
  \item[] Give a closed form expression for the number of legal variable names of length $n$.
    \begin{enumerate}
      \item[a.] We can get 0 or more letters from {a,b,c} followed by 0 or more letters from {0,1,2,3}.
      \item[b.] We know for a sequence $a_0,a_1,a_2,a_3$, there are $\sum_{n=0}^{\infty}a_n\cdot z^n = F(z)$,
        where $a_n$ represents the number of ways to write a string, n is the length of the sequence, z is a placeholder to make the sum converge, and F(z) is the generating function in closed form.
      \item[c.] For the nth coefficient series: $\sum_{n=0}^{\infty}a_n\cdot z^n = \sum_{n=0}^{\infty}(az)^n = \frac{1}{1-az}$
        \\ Therefore, the generating function for {a,b,c} is $\frac{1}{1-3z}$ and the generating function for {0,1,2,3} is $\frac{1}{1-4z}$
      \item[d.] $\frac{1}{1-4z}\cdot\frac{1}{1-3z} = \frac{A}{1-3z}+\frac{B}{1-4z}$
        \\ $\frac{A}{1-3z}+\frac{B}{1-4z} = \frac{A(1-4z)+B(1-3z)}{(1-4z)(1-3z)}$
        \\ $A(1-4z)+B(1-3z) = 1 + 0z$ 
        \\ $A - A(4z) + B - B(3z) = 1 + 0z$
        \\ A+B = 1
        \\ $-A(4z) - B(3z) = 0z$
        \\ A=-3, B=4
      \item[e.] $\frac{-3}{1-3z}+\frac{4}{1-4z} = -3\frac{1}{1-3z}+4\frac{1}{1-4z} 
        \\ = -3\sum_{n=0}^{\infty}(3-z)^n + 4\sum_{n=0}^{\infty}(4z)^n
        \\ = \sum_{n=0}^{infty}-(3)^{n+1}\cdot z^n + \sum_{n=0}^{\infty} 4^{n+1}\cdot z^n
        \\ = \sum_{n=0}^{\infty}(4^{n+1}-3^{n+1})\cdot z^n$
    \end{enumerate}
    Therefore, for a sequence of length n, there are $4^{n+1} - 3^{n+1}$ to write a variable name.
\end{enumerate}

\end{document}
